\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-03-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updated

\begin{figure}
\centering
\subfigure[flow at t=1000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf}}\\[2mm]%
\subfigure[flow at t=2500]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}}%
\caption{As the flow progress, t=1000(a), a tip start to appears, at t=2500(b)}
\label{fig:1b_homoheleshaw_3}
\end{figure}

@@

>>>>

\begin{figure}
\centering
\subfigure[flow at t=1000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf}}\\[2mm]%
\subfigure[flow at t=2500]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}}%
\caption{Following Fig.\ref{fig:1a_homoheleshaw_3} as the flow progress, t=1000(a), a tip start to appears, at t=2500(b)}
\label{fig:1b_homoheleshaw_3}
\end{figure}

@@

As can been seen from the Fig.\ref{fig:1a_homoheleshaw_3},\ref{fig:1b_homoheleshaw_3} and Fig.\ref{fig:1c_homoheleshaw_3} there is a significant difference on the flow pattern when the mobility ratio is $3$ and when it is $10$. As the set-up of the simulation remained the same, fingers will be more profound and will start develop faster when the $MR=10$ compared to the uniform front that is developing when the $MR=3$ for the same time steps.
